### 2018-10-10 Paper/Paper.tex
Cleaned up tex file

\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{geometry}
\usepackage{xcolor,graphicx}
\usepackage[subfolder,cleanup]{gnuplottex}
%\usepackage{amsthm}
%\usepackage{enumitem}
%\usepackage{wrapfig}
%\usepackage{subcaption}
\usepackage{hyperref}
\usepackage{biblatex}

@@

%Impetutus: Want every student to have at least one experiential learning opportunity by the time they graduate.
%Stake from province: 780K received to do this
%
%Examples of experiential learning:
%industry or community agency sponsored research projects
%interactive simulations
%capstone projects
%on-campus work/teaching labs
%performance based learning
%
%Checkmark 1: Student is in a workplace or a simulated workplace.
%This could be a lab or a workstation.  Use of industry standard software.  Case study application.
%Field trips provided that it meets all of the criteria.
%
%Checkmark 2: Student is exposed to authentic demands that improve employability.
%Initiative, communication, conflict resolution, making them use their own initiative to solve
%problems that may arise.
%
%Checkmark 3: Experience is structured, with purposeful and meaningful activities.
%Planning, supervision, guidance, check-in.  There is resource from Reyerson that helps break this down
%This is not just photocopying or filing.
%
%Checkmark 4: Student applies program knowledge.
%Relevance to course learning and encourage students to be flexible.
%
%Checkmark 5: Experience includes self-evaluation and assessment of learning outcomes.
%This is a typical stumbling block and requires that the student is reflective on what was learned and
%how this applies to future learning.  Assessment of the student's work is tied to to the learning outcomes.
%Student's need to be introduced to meaningful reflection.
%
%Checkmark 6: Experience includes formal recognition.
%Recognition has to acknowledge the experience meets the previous five criteria.
%
% HIGH LEVEL IDEAS:
%Case studies - partnership with a pharmaceutical firm to develop in-office posters to explain how a 
%drug works for use by a physician. (Check out RIIPEN website)
%Field trips - design and incorporate activity, conceptualization, and reflection.  A tour of an R&D facility.
%Hackathons - Student-led intensive sessions to solve real-world problems.  Interdisciplinary teams
%to create ideas for a community healthcare initiative.
%
%
%
%Promoting a tapestry of science.

@@

\section{Average Model}

The model for the amplitude in the `average' model is presupposed to have the form
\begin{equation}
\label{average}
	\pdiff{A}{z} = -i\frac{\beta_2}{2}\pdiff[2]{A}{T} - \frac{\epsilon}{2}T^2 A + \frac{g}{2}A
\end{equation}
where $A=A(T,z)$ is the complex amplitude of the pulse
with $\beta_2 \in \mathbb{R}$ defining the dispersion, $\epsilon \in \mathbb{R}$, $\epsilon > 0$, determining the
modulation and $g \in \mathbb{R}$, $g > 0$ giving the gain.  Expression~(\ref{average}) is reminiscent of the 
nonlinear Schr\"odinger equation but linear in $A$ so that the solution can take the form of a Gaussian wavepacket.
Consequently, the ansatz for the amplitude is taken to be a function of the form
\begin{equation}
\label{ansatz}
	A(T,z) = \left(\frac{P_0}{1-i C}\right)^{1/2}\exp
	\left(-\frac{\delta \Omega^2 T^2}{2(1-i C)}\right)\textrm{e}^{i\psi z}
\end{equation}
so that the modulus, $|A|$, and the phase, $A/|A|$, are given by
\begin{align*}
	\left|A\right| &= \left(\frac{P_0}{\sqrt{1 + C^2}}\right)^{1/2}
	\exp\left(-\frac{\delta \Omega^2 T^2}{2(1 + C^2)}\right),&
	\frac{A}{|A|} &= \left(\frac{1+iC}{\sqrt{1+C^2}}\right)^{1/2}\exp
	\left(-i\frac{\delta \Omega^2 T^2 C}{2(1+C^2)}\right)\textrm{e}^{i\psi z}.
\end{align*}
The quantity $C \in \mathbb{R}$ is known as the chirp and contributes a constant phase of $\theta$ where
$2\theta = \arctan C$, $P_0$ is the maximum value of $|A|^2$ at $C=0$ (zero chirp), $\psi \in \mathbb{R}$
is the accumulated phase, and $\delta\Omega$ is the spectral half-width of $|A|^2$ 
since\footnote{If $f(t) = \textrm{e}^{-\alpha t^2}$ then $\hat{f}(\omega) = \frac{1}{2\pi}\int_{\mathbb{R}}
f(t)\textrm{e}^{-i\omega t}\, \df t = \frac{1}{2\pi} (\frac{\pi}{\alpha})^{1/2}\textrm{e}^{-\omega^2/4\alpha}$.}
\[
	\hat{A}(\omega,z) = \frac{1}{2\pi}\int_{-\infty}^\infty A(t,z) \textrm{e}^{-i\omega t}\, \df t
	= \left(\frac{P_0}{2\pi\delta \Omega^2}\right)^{1/2}
	\exp\left(-\frac{(1-i C)\omega^2}{2\delta \Omega^2}\right) \textrm{e}^{i\psi z},
\]
and $|\hat{A}(\delta\Omega,z)|^2 = \textrm{e}^{-1}|\hat{A}(0,z)|^2$.  The corresponding half-width of the
pulse duration comes from the expression for $|A|$ and gives
\begin{equation}
\label{duration}
	\delta T = \frac{\sqrt{1+C^2}}{\delta \Omega}.
\end{equation}

@@

@@

\subsection{Dispersion}
Within the laser cavity, the dispersion is dominated by the chirped fibre Bragg grating (CFBG).  In comparision,
the dispersion due to the fibre is negligible.\footnote{A $10$ cm chirped grating can provide as much dispersion 
as $300$ km of fibre~\cite{agrawal2002}.} The dispersive terms of \eqref{eq:nlse} give
\begin{align}
\label{eq:disp}
	\pdiff{A}{z} = -i \frac{\beta_2}{2} \pdiff[2]{A}{T} + \frac{\beta_3}{6} \pdiff[3]{A}{T}
\end{align}
and since dispersion acts in the frequency domain, it is convenient to use the Fourier transform 
of~\eqref{eq:disp}, giving the result that
\begin{align*}
	\pdiff{\FT{A}}{z} &= i\frac{\omega^2}{2}\left(\beta_2 + \frac{\beta_3}{3} \omega\right) \FT{A}.
\end{align*}
The affect of dispersion is then
\begin{align}
\label{eq:dispersion}
	D(A) &= \FTi{\textrm{e}^{i \omega^2 L_D(\beta_2 + \beta_3 \omega/3)/2} \FT{A}}.
\end{align}
For a highly dispersive media the third order effects may need to be considered~\cite{agrawal2013, litchinitser}.
However, for simplicity in the basic model, the third order effect will be neglected so we set $\beta_3=0$ for 
the subsequent analysis~\cite{agrawal2013, ferreira}.

@@

\end{gnuplot}
\caption{}
\label{fig:}
\end{figure}

@@

\begin{figure}[htbp]
\centering
\begin{gnuplot}[terminal=epslatex, terminaloptions={color size 6in,3.7in lw 3}]
set grid
set xl '$s$'
set yl '$b$'
set cbl 'Error'
set xr [0:1.5]
set view map

set palette defined ( 0 '#D73027',\
    	    	      1 '#F46D43',\
		      2 '#FDAE61',\
		      3 '#FEE090',\
		      4 '#E0F3F8',\
		      5 '#ABD9E9',\
		      6 '#74ADD1',\
7 '#4575B4' )

set cbr [0:0.5]
sp '../abig.dat' using 1:2:3 w image not
\end{gnuplot}
\caption{Error is calculated by $\displaystyle \frac{\|A(\text{iteration } 75) - A(\text{iteration } 74) \|_2}{\|A(\text{iteration } 74) \|_2}$}
\label{fig:}
\end{figure}

\begin{figure}[htbp]
\centering
\begin{gnuplot}[terminal=epslatex, terminaloptions={color size 6in,3.7in lw 3}]
set grid
set xl '$s$'
set yl '$b$'
set cbl 'Energy'
set xr [0:1.5]
set view map

set palette defined ( 0 '#D73027',\
    	    	      1 '#F46D43',\
		      2 '#FDAE61',\
		      3 '#FEE090',\
		      4 '#E0F3F8',\
		      5 '#ABD9E9',\
		      6 '#74ADD1',\
7 '#4575B4' )

set cbr [0:0.25]
sp '../abig.dat' using 1:2:4 w image not
\end{gnuplot}
\caption{}
\label{fig:}
\end{figure}

\begin{figure}[htbp]
\centering
\begin{gnuplot}[terminal=epslatex, terminaloptions={color size 6in,3.7in lw 3}]
S(x) = exp(-0.511444 * x + 0.0017412)
E(x, y) = -y**2 * log(a * y**2 * S(x)**2) * S(x)**2 / (y**2 * S(x)**2 - 1)
a = 30

set grid
set pm3d map
set isosamples 100, 100
set hidden3d
set contour surface
set cntrparam levels incremental 0, 0.1, 1.5
set palette rgbformulae 22, 13, -31

set palette defined ( 0 '#D73027',\
    	    	      1 '#F46D43',\
		      2 '#FDAE61',\
		      3 '#FEE090',\
		      4 '#E0F3F8',\
		      5 '#ABD9E9',\
		      6 '#74ADD1',\
7 '#4575B4' )

>>>>

\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{geometry}
\usepackage{xcolor,graphicx}
\usepackage[subfolder,cleanup]{gnuplottex}
%\usepackage{amsthm}
%\usepackage{enumitem}
%\usepackage{wrapfig}
\usepackage{subcaption}
\usepackage{hyperref}
\usepackage{biblatex}

@@

@@

\section{Average Model}
The model for the amplitude in the `average' model is presupposed to have the form
\begin{equation}
\label{average}
	\pdiff{A}{z} = -i\frac{\beta_2}{2}\pdiff[2]{A}{T} - \frac{\epsilon}{2}T^2 A + \frac{g}{2}A
\end{equation}
where $A=A(T,z)$ is the complex amplitude of the pulse with $\beta_2 \in \mathbb{R}$ defining the dispersion, $\epsilon \in \mathbb{R}$, $\epsilon > 0$, determining the modulation and $g \in \mathbb{R}$, $g > 0$ giving the gain. Expression~(\ref{average}) is reminiscent of the nonlinear Schr\"odinger equation but linear in $A$ so that the solution can take the form of a Gaussian wavepacket. Consequently, the ansatz for the amplitude is taken to be a function of the form
\begin{equation}
\label{ansatz}
	A(T,z) = \left(\frac{P_0}{1-i C}\right)^{1/2}\exp
	\left(-\frac{\delta \Omega^2 T^2}{2(1-i C)}\right)\textrm{e}^{i\psi z}
\end{equation}
so that the modulus, $|A|$, and the phase, $A/|A|$, are given by
\begin{align*}
	\left|A\right| &= \left(\frac{P_0}{\sqrt{1 + C^2}}\right)^{1/2}
	\exp\left(-\frac{\delta \Omega^2 T^2}{2(1 + C^2)}\right),&
	\frac{A}{|A|} &= \left(\frac{1+iC}{\sqrt{1+C^2}}\right)^{1/2}\exp
	\left(-i\frac{\delta \Omega^2 T^2 C}{2(1+C^2)}\right)\textrm{e}^{i\psi z}.
\end{align*}
The quantity $C \in \mathbb{R}$ is known as the chirp and contributes a constant phase of $\theta$ where $2\theta = \arctan C$, $P_0$ is the maximum value of $|A|^2$ at $C=0$ (zero chirp), $\psi \in \mathbb{R}$ is the accumulated phase, and $\delta\Omega$ is the spectral half-width of $|A|^2$ since\footnote{If $f(t) = \textrm{e}^{-\alpha t^2}$ then $\hat{f}(\omega) = \frac{1}{2\pi}\int_{\mathbb{R}} f(t)\textrm{e}^{-i\omega t}\, \df t = \frac{1}{2\pi} (\frac{\pi}{\alpha})^{1/2}\textrm{e}^{-\omega^2/4\alpha}$.}
\[
	\hat{A}(\omega,z) = \frac{1}{2\pi}\int_{-\infty}^\infty A(t,z) \textrm{e}^{-i\omega t}\, \df t
	= \left(\frac{P_0}{2\pi\delta \Omega^2}\right)^{1/2}
	\exp\left(-\frac{(1-i C)\omega^2}{2\delta \Omega^2}\right) \textrm{e}^{i\psi z},
\]
and $|\hat{A}(\delta\Omega,z)|^2 = \textrm{e}^{-1}|\hat{A}(0,z)|^2$. The corresponding half-width of the pulse duration comes from the expression for $|A|$ and gives
\begin{equation}
\label{duration}
	\delta T = \frac{\sqrt{1+C^2}}{\delta \Omega}.
\end{equation}

@@

\end{gnuplot}
\caption{}
\label{fig:average}
\end{figure}

@@

\subsection{Dispersion}
Within the laser cavity, the dispersion is dominated by the chirped fibre Bragg grating (CFBG). In comparison, the dispersion due to the fibre is negligible.\footnote{A $10$ cm chirped grating can provide as much dispersion as $300$ km of fibre~\cite{agrawal2002}.} The dispersive terms of \eqref{eq:nlse} give
\begin{align}
\label{eq:disp}
	\pdiff{A}{z} = -i \frac{\beta_2}{2} \pdiff[2]{A}{T} + \frac{\beta_3}{6} \pdiff[3]{A}{T}
\end{align}
and since dispersion acts in the frequency domain, it is convenient to use the Fourier transform of~\eqref{eq:disp}, giving the result that
\begin{align*}
	\pdiff{\FT{A}}{z} &= i\frac{\omega^2}{2}\left(\beta_2 + \frac{\beta_3}{3} \omega\right) \FT{A}.
\end{align*}
The affect of dispersion is then
\begin{align}
\label{eq:dispersion}
	D(A) &= \FTi{\textrm{e}^{i \omega^2 L_D(\beta_2 + \beta_3 \omega/3)/2} \FT{A}}.
\end{align}
For a highly dispersive media the third order effects may need to be considered~\cite{agrawal2013, litchinitser}. However, for simplicity in the basic model, the third order effect will be neglected so we set $\beta_3=0$ for the subsequent analysis~\cite{agrawal2013, ferreira}.

@@

@@

\begin{figure}[htbp]
\centering
\begin{subfigure}[]{\textwidth}
\begin{gnuplot}[terminal=epslatex, terminaloptions={color size 6in,3.7in lw 3}]
set grid
set xl '$s$'
set yl '$b$'
set cbl 'Error'
set xr [0:1]
set view map

load '/home/brady/Templates/YGB.p'

set cbr [0:0.75]
sp '../On.dat' using 1:2:3 w image not
\end{gnuplot}
\caption{}
\label{fig:}
\end{subfigure}
\begin{subfigure}[]{\textwidth}
\begin{gnuplot}[terminal=epslatex, terminaloptions={color size 6in,3.7in lw 3}]
set grid
set xl '$s$'
set yl '$b$'
set cbl 'Error'
set xr [0:0.2]
set view map

load '/home/brady/Templates/YGB.p'

set cbr [0:0.75]
sp '../Zoom01.dat' using 1:2:3 w image not
\end{gnuplot}
\caption{}
\end{subfigure}
\caption{Error is calculated by $\displaystyle \frac{\|A(\text{iteration } 75) - A(\text{iteration } 74) \|_2}{\|A(\text{iteration } 74) \|_2}$}
\label{fig:}
\end{figure}

\begin{figure}[htbp]
\centering
\begin{gnuplot}[terminal=epslatex, terminaloptions={color size 6in,3.7in lw 3}]
load '/home/brady/Templates/YGB.p'
S(x) = exp(-0.511444 * x + 0.0017412)
E(x, y) = -y**2 * log(a * y**2 * S(x)**2) * S(x)**2 / (y**2 * S(x)**2 - 1)
a = 30

set grid
set pm3d map
set isosamples 100, 100
set hidden3d
set contour surface
set cntrparam levels incremental 0, 0.1, 1.5
